On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2023-10-11 Manuscript/manuscript.tex
Added year effect plots and fixed std dev typos

\begin{table}
  \centering
  \caption{2019 vs 2022 compares data from the same athletes who competed at the
  2019 and 2022 World Track and Field Championships. 2022 vs 2023 compares data
  from the same athletes who competed at the 2022 and 2023 World Track and Field
  Championships. National vs International compares data from the same athletes
  who competed at 2022 national-level championships and the 2022 World Track and
  Field Championships.}
  \begin{tabular}{c c c c c} 
   \toprule
   Comparison & Permutation & Asymptotic \\ 
   \midrule
   2019 vs 2022 & $2.8\cdot10^{-2}$ & $2.9\cdot10^{-3}$ \\
   2022 vs 2023 & $1.1\cdot10^{-2}$ & $3.1\cdot10^{-3}$ \\
   2022 National vs International & $2\cdot10^{-6}$ & $1.1\cdot10^{-3}$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Clusrankresults}
\end{table}

Table~\ref{tab:Clusrankresults} shows the results generated from both the 
permutation and asymptotic rank-based tests for the three comparisons, 
as discussed previously in Section~\ref{sec:rank}. The national versus international
comparison produced lower p-values than the 2019 versus 2022 comparison, with the
national vs international permutation test producing a p-value of $2\cdot10^{-6}$.
This is a highly significant test result and shows that athletes who competed at the
2022 World Track and Field Championships were on average, significantly faster
at reacting than they were just a few months prior. For the 2019 versus 2022
same athlete comparison with permutation test, the p-value was 
$2.9\cdot10^{-3}$, which is significant at $\alpha = 0.01$. The result of
comparing 2022 and 2023 was very similar to the above result, as the p-value
from the permutation test was $3.0\cdot10^{-3}$. Taken together, these three
tests help show that athletes competing at the 2022 World Track and Field
Championships had faster reaction times than when they had competed previously.

@@

The estimated parameters of the GLMM model from our analysis are shown in 
Table~\ref{tab:Gamma_parameters}. These statistics reflect the inclusion of 2022
in our analysis and shows the three models we considered. The standard deviation
of the heat effect is $\sigma_h^2$, the standard deviation of the venue effect
is $\sigma_v^2$, the intercept is $\alpha$ and we report $\sqrt{\phi}$ as the
standard deviation of the dispersion parameter $\phi$
\jy{read what you wrote. These are variances not sd. Do not start a sentence
  with a symbol (see my writing guidelines).}
\of{Resolved}
The GLMM with both venue and heat random
effects was the best model as evidenced by a decrease in the AIC compared to the
other models with only one random effect. 
Thus, results from the GLMM with both venue and heat random effects
will be presented throughout the rest
of the paper.

@@

\begin{table}
  \centering
  \caption{AIC and estimated parameters for the three models fitted to all the
    data.}
  \label{tab:Gamma_parameters}
  \begin{tabular}{c c c c c c}
      \toprule
      Model & AIC & $\sigma_h^2$ & $\sigma_v^2$ & $\alpha$ & $\sqrt{\phi}$ \\
      \midrule
      Venue Effect Only & $-2023.5$ &   & 0.054 & $-1.871$ & 0.150\\
      Heat Effect Only & $-2070.7$ & 0.073 &  & $-1.890$ & 0.135\\
      Venue and Heat Effect & $-2075.7$ & 0.057 & 0.040 & $-1.880$ & 0.134\\
      \bottomrule
  \end{tabular}
\end{table}

Two aims of this section are to determine how extreme a reaction time below
0.1 seconds is, and to determine how the exclusion of 2022 could alter the results.
Using the gamma function with link set to log, the probability of the reaction 
time being less than 0.1 seconds can be calculated in R using the methods 
described in Section~\ref{sec:glmm}. A simulation size of $10,000,000$ was 
chosen to estimate the probability of observing a reaction time below 
two thresholds: 0.1 and 0.08.

@@

\jy{be consistent in using scienfit format of numbers; 0.0001 vs $10^{-4}$}
\of{In our meeting you said to convert scientific notation like $10^{-2}$ to 
0.01, and I agree I think 0.01 makes much more sense. So should I convert
everything to decimals or scientific notation?}

>>>>

\begin{table}
  \centering
  \caption{2019 vs 2022 compares data from the same athletes who competed at the
  2019 and 2022 World Track and Field Championships. 2022 vs 2023 compares data
  from the same athletes who competed at the 2022 and 2023 World Track and Field
  Championships. National vs International compares data from the same athletes
  who competed at 2022 national-level championships and the 2022 World Track and
  Field Championships.}
  \begin{tabular}{c c c c c} 
   \toprule
   Comparison & Permutation & Asymptotic \\ 
   \midrule
   2019 vs 2022 & $0.028$ & $0.003$ \\
   2022 vs 2023 & $0.011$ & $0.003$ \\
   2022 National vs International & $2\cdot10^{-6}$ & $0.001$ \\
   \bottomrule
  \end{tabular}
  \label{tab:Clusrankresults}
\end{table}

Table~\ref{tab:Clusrankresults} shows the results generated from both the 
permutation and asymptotic rank-based tests for the three comparisons, 
as discussed previously in Section~\ref{sec:rank}. The national versus international
comparison produced lower p-values than the 2019 versus 2022 comparison, with the
national vs international permutation test producing a p-value of $2\cdot10^{-6}$.
This is a highly significant test result and shows that athletes who competed at the
2022 World Track and Field Championships were on average, significantly faster
at reacting than they were just a few months prior. For the 2019 versus 2022
same athlete comparison with permutation test, the p-value was 
$0.003$, which is significant at $\alpha = 0.01$. The result of
comparing 2022 and 2023 was very similar (but not exactly the same) to the above
result, as the p-value from the permutation test was $0.003$. Taken together, these three
tests help show that athletes competing at the 2022 World Track and Field
Championships had faster reaction times than when they had competed previously.

@@

\begin{table}
  \centering
  \caption{AIC and estimated parameters for the three models fitted to all the
    data.}
  \label{tab:Gamma_parameters}
  \begin{tabular}{c c c c c c}
      \toprule
      Model & AIC & $\sigma_h$ & $\sigma_v$ & $\alpha$ & $\sqrt{\phi}$ \\
      \midrule
      Venue Effect Only & $-2023.5$ &   & 0.054 & $-1.871$ & 0.150\\
      Heat Effect Only & $-2070.7$ & 0.073 &  & $-1.890$ & 0.135\\
      Venue and Heat Effect & $-2075.7$ & 0.057 & 0.040 & $-1.880$ & 0.134\\
      \bottomrule
  \end{tabular}
\end{table}

The estimated parameters of the GLMM model from our analysis are shown in 
Table~\ref{tab:Gamma_parameters}. These statistics reflect the inclusion of 2022
in our analysis and shows the three models we considered. The standard deviation
of the heat effect is $\sigma_h$, the standard deviation of the venue effect
is $\sigma_v$, the intercept is $\alpha$ and we report $\sqrt{\phi}$ as the
square root of the dispersion parameter $\phi$
\jy{read what you wrote. These are variances not sd. Do not start a sentence
  with a symbol (see my writing guidelines).}
\of{Actually Resolved}
The GLMM with both venue and heat random effects was the best model as evidenced
by a decrease in the AIC compared to the other models with only one random effect. 
Thus, results from the GLMM with both venue and heat random effects will be 
presented throughout the rest of the paper.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics{ComparisonOfVenueEffects}
  \caption{The venue effects from 1999 to 2023 for the data including 2022 (top)
  and excluding 2022 (bottom)}
  \label{fig:VenueEffects}
\end{figure}

Figure~\ref{fig:VenueEffects} shows the venue effects from 1999 to 2023 based
on the full model both with and without 2022.  As this graph does not show heat
effects, the estimates may not align exactly with the box plot presented in
figure~\ref{fig:Boxplot}.  The venue effect for 2022 is lower than any other
effect, confirming that 2022 was a low outlier.  Two aims of this section are to
determine how extreme a reaction time below 0.1 seconds is, and although the
venue effects did not differ significantly, to determine how the exclusion of 
2022 could alter the results. Using the gamma function with \texttt{link = log},
the probability of the reaction time being less than 0.1 seconds can be 
calculated in R using the methods described in Section~\ref{sec:glmm}. A 
simulation size of $10,000,000$ was chosen to estimate the probability of 
observing a reaction time below two thresholds: 0.1 and 0.08.

@@

\jy{be consistent in using scienfit format of numbers; 0.0001 vs $10^{-4}$}
\of{I think we should be good now, let me know if there is anything else}
